Including EW and mixed QCD-EW corrections into PDF fits

### 2020-03-31 paper/sec-introduction.tex
Intro WIP

The Large Hadron Collider (LHC)

ERN

The impact of EW corrections to LHC data.\\
How to do that consistently, include systematically EW corrections, blabla.\\
Outline a possible strategy to deal with EW correction in LHC observables (FSR, PHOTOS, dressed/born, ...).\\
Pinappl kills amcfast and mcgrid, replace applgrid and fastnlo.\\

>>>>

With the recent completion of Run II, the Large Hadron Collider (LHC) has 
accumulated data from an integrated luminosity of approximately 
150~fb$^{-1}$~\cite{Mangano:2020icy}. This represents only a small fraction of 
the anticipated 3000 fb$^{-1}$ that will eventually be recorded in the 
forthcoming twenty years of LHC operation. Nevertheless the statistical 
uncertainty of the data has already shrunk to unprecedentedly small values,
typically 1\% or less, a fact that will allow for precision tests of the 
Standard Model (SM) and for indirect searches of New Physics only if 
theoretical predictions become comparatively precise. This entails the 
computation of additional higher-order contributions to the fixed-order 
coupling-constant perturbative expansion, on the one hand, and an increasingly 
sophisticated determination of the Parton Distribution Functions (PDFs) of the 
proton~\cite{Gao:2017yyd}, on the other hand.

In the first respect, because Quantum Chromodynamics (QCD) dominates the 
interactions occurring within colliding protons at the LHC, much effort 
has been devoted to the computation of higher-order QCD corrections: 
fully-differential next-to-leading order (NLO) results, possibly matched to the
parton shower, are currently automated in various general-purpose
Monte Carlo generators~\cite{Gleisberg:2008ta,Alwall:2014hca,Bellm:2015jjp}, 
while an increasing number of next-to-next-to-leading order (NNLO) predictions 
are becoming available for processes with various degrees of inclusiveness
(see {\it e.g.}~\cite{Amoroso:2020lgh} and references therein). The computation
of higher-order corrections in the Electroweak (EW) theory has 
witnessed a comparatively less comprehensive progress. Nevertheless frameworks 
were developed in which the QCD and EW couplings are simultaneously treated as 
small parameters in the perturbative expansion, and the computation of 
theoretical predictions, accurate to NLO (including mixed-coupling QCD+EW 
terms), is automated~\cite{Biedermann:2017yoi,Frederix:2018nkq}.

In the second respect, contemporary PDF
sets~\cite{Harland-Lang:2014zoa,Ball:2017nwa,Hou:2019efy}
incorporate a significant amount of LHC data, which is analysed with NNLO QCD 
theory by default. No EW corrections are included in the theoretical 
description of the experimental observables to which PDFs are optimised,
except for QED effects if a photon PDF is 
determined~\cite{Schmidt:2015zda,Bertone:2017bme,Harland-Lang:2019pla}. 
The resulting relative PDF uncertainy --- 
which accounts only for the uncertainty of the data and of the 
methodology inherent to each PDF determination --- can be as low as 1\% at the 
EW scale~\cite{Ball:2017nwa}. Theoretical uncertainties, possibly of comparable 
size ({\it e.g.} from missing higher-order terms in the perturbative expansion),
can also be included in a PDF determination and represented into PDF 
uncertainties~\cite{AbdulKhalek:2019bux,AbdulKhalek:2019ihb}.
This leads to a noticeable improvement of PDF accuracy, in that the overall 
statistical quality of the fit increases, at the price of a modest 
deterioration of PDF precision, in that PDF uncertainties are slightly inflated.

The two respects are intertwined: PDFs provide a way of obtaining a prediction
for a given process in terms of other processes, therefore the accuracy and 
precision with which PDFs are able to make predictions crucially depend on 
the accuracy of the perturbative computation used in the PDF determination
(matched to the precision of the data). Electroweak (including mixed QCD+EW) 
effects should therefore naturally be included in a PDF determination. The 
reason is twofold. First, one expects NNLO QCD and NLO EW corrections to be of 
comparable size because, at the EW scale, the QCD and EW coupling constants 
become similar, $\alpha_s^2\sim \alpha$. If NNLO QCD corrections are included 
by default in PDF determinations, NLO EW and NLO EW+QCD corrections should be 
taken into account on the same footing. Second, the virtual exchange of soft or 
collinear weak bosons leads to Sudakov 
logarithms~\cite{Denner:2000jv,Denner:2001gw},
which can make the coefficients of the EW series grow faster than 
their QCD counterparts. Such a behaviour becomes relevant in
phase-space regions associated with large mass scales (roughly of the order
of the TeV), where several LHC data sets ({\it e.g.} $Z$ boson transverse 
momentum distributions) enter both the determination of PDFs and the search
for New Physics.

The systematic inclusion of EW corrections in a PDF determination entails
the solution of two separate problems. efficiency (produce lookup tables)
and consistency (avoid double counting).
This paper addresses the first problem. How? By developing Pinanppl

How to do that consistently, include systematically EW corrections, blabla.\\
Outline a possible strategy to deal with EW correction in LHC observables (FSR, PHOTOS, dressed/born, ...).\\
Pinappl kills amcfast and mcgrid, replace applgrid and fastnlo.\\
